Models

### 2021-10-06 analysis/05_model_metrics.Rmd
add interaction models

  fit <- data %>%
    filter(metric == metric_name) %>%
    mutate(year_scaled = scale(year)) %>%
    qlmer(formula = formula, data = ., ...)

@@

usethis::use_data(metric_model_table)
pins::pin(metric_model_table, board = "github")
```
#### Process Model Output

>>>>

  fit <- data %>%
    filter(metric == metric_name) %>%
    mutate(year_scaled = scale(year),
           duration_scaled = scale(duration, scale = FALSE),
           startyear_scaled = scale(startyear, scale = FALSE)) %>%
    qlmer(formula = formula, data = ., ...)

@@

usethis::use_data(metric_model_table)
pins::pin(metric_model_table, board = "github")
```

Models with interactions
```{r}
int_raw_value_mods <- tibble(metric_name = c("SES_FRic", "SES_FEve", "SES_FDiv", "FRic", "FEve", "FDiv", "Jaccard_base"), 
                         base_dur = "value ~ year_scaled + duration_scaled*year_scaled + (year_scaled|study_id/rarefyID)",
                         taxa_dur = "value ~ year_scaled + duration_scaled*year_scaled + (year_scaled|study_id/rarefyID) + (year_scaled|taxa)",
                         realm_dur = "value ~ year_scaled + duration_scaled*year_scaled + (year_scaled|study_id/rarefyID) + (year_scaled|realm)",
                         climate_dur = "value ~ year_scaled + duration_scaled*year_scaled + (year_scaled|study_id/rarefyID) + (year_scaled|climate)",
                         base_srt = "value ~ year_scaled + startyear_scaled*year_scaled + (year_scaled|study_id/rarefyID)",
                         taxa_srt = "value ~ year_scaled + startyear_scaled*year_scaled + (year_scaled|study_id/rarefyID) + (year_scaled|taxa)",
                         realm_srt = "value ~ year_scaled + startyear_scaled*year_scaled + (year_scaled|study_id/rarefyID) + (year_scaled|realm)",
                         climate_srt = "value ~ year_scaled + startyear_scaled*year_scaled + (year_scaled|study_id/rarefyID) + (year_scaled|climate)") %>%
  pivot_longer(cols = c(base_dur, taxa_dur, realm_dur, climate_dur, base_srt, taxa_srt, realm_srt, climate_srt), 
               names_to = "model_id", values_to = "formula")

# int_log_value_mods <- tibble(metric_name = c("S"), 
#                          base = "logvalue ~ year_scaled + (year_scaled|study_id/rarefyID)",
#                          taxa = "logvalue ~ year_scaled + (year_scaled|study_id/rarefyID) + (year_scaled|taxa)",
#                          realm = "logvalue ~ year_scaled + (year_scaled|study_id/rarefyID) + (year_scaled|realm)",
#                          climate = "logvalue ~ year_scaled + (year_scaled|study_id/rarefyID) + (year_scaled|climate)") %>%
#   pivot_longer(cols = c(base, taxa, realm, climate), names_to = "model_id", values_to = "formula")

# mods <- bind_rows(raw_value_mods, log_value_mods) %>% 
#   select(metric_name, formula, model_id)

#Fit models with base settings
int_mod_results <- pmap_dfr(int_raw_value_mods, get_model, data = model_data)

#get the models that had convergence warnings
bad_models <- int_mod_results %>%
  select(metric, model_id, warning) %>% 
  filter(!is.na(warning)) %>% 
  distinct() %>%
  left_join(int_raw_value_mods, by = c("metric" = "metric_name", "model_id")) 
```

#### Process Model Output
